Managing variability in software systems

### 2021-05-28 Paper.tex
extended conclusion

\section{Conclusion}
In this document we have given a short introduction to the origin of variability, how to model it and what patterns exist as well as look over work related to these topics. \\

@@

For further information we refer the reader to the references, especially \cite{b2}, which gives a more in depth overview, and \cite{b6}, which compares different approaches to variability modelling.

>>>>

\section{Conclusion}
In this document we have given a short introduction to managing variability in software systems. We do this by establishing the origin of variability, how to model it with either feature modeling or decision modeling as well as what patterns of variability exist in addition to looking over work related to these topics and finally presenting the challenges. \\

Variability is intruduced early in the developement of a new product and can have four main origins: variation in function, variation in data, variation in technology and variation in environment.
This variability can then be modelled via either one of the main approaches, namely feature modeling or decision modeling.
The modelled variability mainly fall in three categories and can vary its binding time as described in section 5.\\

@@

By now the scientific community has a solid understanding of variability in software systems and variability modelling has become a broadly used tool.
